Separating Use and Reuse to Improve Both

### 2017-05-08 FACS/Intro.tex
Overview

\item {\bf Allowing reuse even when subtyping is impossible:} 
In some situations a subclass contains methods whose signatures 
are incompatible with the superclass, yet inheritance is still
possible. A typical example, which was illustrated by Cook et al., are 
classes with \emph{binary methods}~\cite{}.

@@

>>>>

\item {\bf Allowing inheritance/reuse even when subtyping is impossible:} 
In some situations a subclass contains methods whose signatures 
are incompatible with the superclass, yet inheritance is still
possible. A typical example, which was illustrated by Cook et al., are 
classes with \emph{binary methods}~\cite{}.

@@

\name solution for the leaking problem shows

\subsection{Preventing Unintended Subtyping}
As stated in Section~\ref{} a benefit of a nominally typed OO language
that separates inheritance from subtyping is that it is possible to 
have reuse, while preventing unintended subtyping.

An iconic example on why connecting inheritance/code reuse and
subtpying is problematic is provided by the
historic\cite{LaLonde:1991:SSS:110673.110679}: A reasonable
implementation for a \Q@Set@ may be easy to extend into a \Q@Bag@
keeping tracks of how many times an element occurs.  We would just add
some state and override a couple of methods.\bruno{Are we going to
  present this example in the paper solved in 42, for example? 
I think I would expect to see it.}

However, our subclassing would break Liskov substitution principle (LSP)~\cite{martin2000design}: not all bags are sets!
Of course, one could retroactivelly fix this problem by introducing \Q@AbstractSetOrBag@
and making both \Q@Bag@ and \Q@Set@ inherit from it.
This looks unnatural, since \Q@Set@ would extend it without adding anything,
and we would be surprised to find a use of the type \Q@AbstractSetOrBag@.
Worst, if we was to constantly apply this mentalty, we would introduce a very high number
of abstract classes that are not supposed to be used as types, and that will clutter the 
public interface of our classes and our code project as a whole.

\begin{lstlisting}
class Set {.../* Elem put() boolean isIn(Elem)*/ ...}
class Bag extends Set{.../*override something to keep track of duplications*/..}
\end{lstlisting}

but now,

\begin{lstlisting}
Set mySet=new Bag(); //OK for the type system but not for LSP
\end{lstlisting}

as a pleasaruble accident, avoid such code gift us simple support for
This type and (in the extensions with nested classes seen later)
family polimporphism.
